MATH 3610 - Project \#1

### 2015-10-01 proj1.tex
Final commit

\section{Stochastic Model}
\subsection{A naive model}
\par At first, we made a simple, arbitrary stochastic model just to get a rough idea of how the disease would spread. Over the course of 5 months, we would look at the spread of the disease given certain conditions. Every citizen fell into an age category, according to demographic figures from \emph{areaConnect} \cite{areconnect}. Then, to model the spread, we associated arbitrary recovery rates, complication rates and number of people talked to per month to each age group, giving us the following table:
\begin{figure}[H]
\centering
\begin{tabular}{c|c|c|c|c}
Age group & Heal rate & Complication chance & Connectivity & Population percentage\\ \hline
Kids & 0.5 & 0.2 & 20 & 10\%\\
Teens & 0.4 & 0.1 & 30 & 40\%\\
Adults & 0.3 & 0.3 & 25 & 40\%\\
Seniors & 0.2 & 0.7 & 10 & 10\%
\end{tabular}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{tabular}{c|c|c|c|c}
		Age group & Heal rate & Complication chance & Connectivity & Population percentage\\ \hline
		Junior & 0.9 & 0.05 & 25 & 60\%\\
		Adults & 0.9 & 0.2 & 15 & 30\%\\
		Seniors & 0.9 & 0.75 & 5 & 10\%
	\end{tabular}
	\caption{More justified attributes for age groups}
	\label{fig:justified-values}
\end{figure}

Here are a handful of runs for different vaccination strategies:
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-novax.png}
		\caption{No vaccination policy}
	\end{subfigure}~
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-randvax.png}
		\caption{Random vaccination policy}
	\end{subfigure}\\
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-juniors.png}
		\caption{Prioritization of kids and teens}
	\end{subfigure}~
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-seniors.png}
		\caption{Prioritization of seniors}
	\end{subfigure}
	\caption{Model runs}
	\label{fig:modelout}
\end{figure}

@@

\subsection{An explanation}
As we saw in Figure~\ref{fig:modelout}

>>>>

\section{Stochastic Model}
\subsection{A naive model}
\par At first, we made a simple, arbitrary stochastic model just to get a rough idea of how the disease would spread. Over the course of 5 months, we would look at the spread of the disease given certain conditions. Every citizen fell into an age category, according to demographic figures from \emph{areaConnect} \cite{areconnect}. Then, to model the spread, we associated arbitrary recovery rates, complication rates and number of people talked to per month to each age group, giving us the following table:
\begin{figure}[h!]
\centering
\begin{tabular}{c|c|c|c|c}
Age group & Heal rate & Complication chance & Connectivity & Population percentage\\ \hline
Kids & 0.5 & 0.2 & 20 & 10\%\\
Teens & 0.4 & 0.1 & 30 & 40\%\\
Adults & 0.3 & 0.3 & 25 & 40\%\\
Seniors & 0.2 & 0.7 & 10 & 10\%
\end{tabular}
\caption{Initial citizen attributes}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\begin{tabular}{c|c|c|c|c}
		Age group & Heal rate & Complication chance & Connectivity & Population percentage\\ \hline
		Junior & 0.9 & 0.05 & 25 & 60\%\\
		Adults & 0.9 & 0.2 & 15 & 30\%\\
		Seniors & 0.9 & 0.75 & 5 & 10\%
	\end{tabular}
	\caption{More justified attributes for age groups}
	\label{fig:justified-values}
\end{figure}

Here are a handful of runs for different vaccination strategies:
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-novax.png}
		\caption{No vaccination policy}
	\end{subfigure}~
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-randvax.png}
		\caption{Random vaccination policy}
	\end{subfigure}\\
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-juniors.png}
		\caption{Prioritization of kids and teens}
	\end{subfigure}~
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/Weekly-seniors.png}
		\caption{Prioritization of seniors}
	\end{subfigure}
	\caption{Model runs}
	\label{fig:modelout}
\end{figure}

@@

\subsection{Analysis}
\par As we saw in Figure~\ref{fig:modelout}, vaccination policies don't actually impact the spread of the disease too much. Rather, it seems to be more helpful for damage control. We see from the 4 graphs in Figure~\ref{fig:modelout} the peak infection rate seems to stay near 10\% regardless of the vaccination policy. On the other hand, it seems to help for damage control because even though the infection rate stays the same, when we vaccinate more seniors, fewer people end up hospitalized than when we target more juniors. But surprisingly, the random vaccination policy consistently came out on top. This peaked our interest, so we ran many simulations comparing the three models. Figure~\ref{fig:10outs} shows the outputs side by side. We see that the random policy actually puts just about as many people in the hospital as the policy that targets seniors, while keeping the peak infection rate actually lower than all the policies.

\begin{figure}[h!]
\centering
\begin{subfigure}[b]{0.5\textwidth}
\centering
\begin{tabular}{rc|c}
& Peak infection (\%) & Total hospitalizations\\ \cline{2-3}
& 11.1  & 431\\
& 10.62 & 418\\
& 9.47  & 433\\
& 8.9   & 414\\
& 11.11 & 404\\
& 10.24 & 411\\
& 11.35 & 442\\
& 10.59 & 412\\
& 10.88 & 432\\
& 10    & 395\\ \hline
Mean & 10.426 & 419.2
\end{tabular}
\caption{Juniors first}
\end{subfigure}~
\begin{subfigure}[b]{0.5\textwidth}
\centering
\begin{tabular}{rc|c}
& Peak infection (\%) & Total hospitalizations\\ \cline{2-3}
& 10.45 & 389\\
& 10.65 & 376\\
& 10.25 & 419\\
& 10.86 & 388\\
& 10.1  & 384\\
& 11.05 & 373\\
& 9.97  & 377\\
& 9.57  & 383\\
& 10.14 & 363\\
& 9.91  & 367\\ \hline
Mean & 10.295 & 381.9
\end{tabular}
\caption{Seniors first}
\end{subfigure}\\
\begin{subfigure}[b]{0.5\textwidth}
\centering
\begin{tabular}{rc|c}
& Peak infection (\%) & Total hospitalizations\\ \cline{2-3}
& 9.5   & 378\\
& 9.99  & 393\\
& 10.02 & 373\\
& 9.28  & 370\\
& 9.72  & 386\\
& 9.68  & 369\\
& 10.25 & 423\\
& 10.36 & 415\\
& 9.11  & 370\\
& 9.96  & 352\\ \hline
Mean & 9.787 & 382.9
\end{tabular}
\caption{Indiscriminate vaccinations}
\end{subfigure}
\caption{Comparison of 10 runs for different vaccination policies}
\label{fig:10outs}
\end{figure}
